---
title: "12_2_Homework"
author: "Juan Garbayo"
date: "3/3/2022"
output:
  bookdown::html_document2:
    number_sections: no
    toc: true
    toc_depth: 6
    toc_float: false
    toc_collapsed: false
    self_contained: true
    lib_dir: libs
params:
  print_sol: FALSE 
---

```{r, warning= FALSE, message=FALSE}
library(fpp3)
```

# Exercise 1

For this exercise we are going to use the `aus_retail` dataset. You should already be familiar with this dataset, since we used it in the asynchronous session 4. Nonetheless remember you can always use `?aus_retail` in the console to red the details abut the dataset.

The contains a variety of series that that might be filtered using their specific series ID. We will be working the the following Series ID: A3349767W. The following code filters the series for you.

```{r}
retail_series <- aus_retail %>%
  filter(`Series ID` == "A3349767W")

head(retail_series)
```

## 1. Use **an STL decompostition** to calculate the trend-cycle and seasonal indices. If you deem it necessary, adjust the averaging windows.

**NOTE:** remember that the STL decomposition is only applicable to additive schemes, which means you need to transform the data first to obtain an additive scheme. 

## 2. Extract and plot the seasonally adjusted data from the decomposition.

## 3. Use the drift method to produce forecasts of the seasonally adjusted data.

## 4. Use `decomposition_model()` to reseasonalize the results. To compute the seasonal component, use the default seasonal naive proceduree.

## 5. Perform an analysis of the residuals.
